Automated Synthesis of State-Space Digital Systems

### 2016-12-26 cav2017/cav2017.tex
Comments on the tolerances

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\ref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers in the form
\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k\ \ :\ \ \mat{K}_d \in \mathbb{R}^{m \times o}.
\end{equation}
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J \wedge
\mat{B} \in \mathcal{G}_B.
\end{align*}

>>>>

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\ref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers creating a feedback loop in the form
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k\ \ :\ \ \mat{K}_d \in \mathbb{R}^{m \times o}.
\end{equation}
%
where $\mat{K}_d$ are the feedback coefficients.
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}

Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
We presume that the internal model of the plant is an ARMA model, modified by a
state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
as tolerances in the canonical forms outside of the row/column of interests and complicate the 
evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
above for simplicity.
